\textsc{TheHaloMod}: An online calculator for the halo model

### 2020-09-28 paper.tex
Fix Bosch again

First, NFW suggested that concentration is intimately related to the assembly history of halos, which can be summarized as their age or formation time. Physically, this dependence can be understood by the transition from the fast to the slow accretion regime, after which the halo boundary (and its concentration) grow mostly via pseudo-evolution while the scale radius remains more or less constant \citep{Navarro1997, Bullock2001, B2, Wechsler2002, Zhao2003, Dalal2010, Diemer2013, Ludlow2013, Wang2020}. This logic has motivated numerous models based on some quantification of the age of halos \citep[e.g.,][]{Eke2001, Zhao2009, Giocoli2012, Ludlow2014, Ludlow2016, Correa2015b}.

>>>>

First, NFW suggested that concentration is intimately related to the assembly history of halos, which can be summarized as their age or formation time. Physically, this dependence can be understood by the transition from the fast to the slow accretion regime, after which the halo boundary (and its concentration) grow mostly via pseudo-evolution while the scale radius remains more or less constant \citep{Navarro1997, Bullock2001, Bosch2002, Wechsler2002, Zhao2003, Dalal2010, Diemer2013, Ludlow2013, Wang2020}. This logic has motivated numerous models based on some quantification of the age of halos \citep[e.g.,][]{Eke2001, Zhao2009, Giocoli2012, Ludlow2014, Ludlow2016, Correa2015b}.
